Crowded Star Fields \\ \bf{Obviously need a better title}

### 2012-04-04 paper/ms.tex
edited document
A small amount of writing listing the unknowns

\title{A Document}
\author{Brendon J. Brewer}

@@

$3^{+1}_{-1}$

It's

>>>>

\title{Crowded Star Fields \\ \bf{Obviously need a better title}} 
\author{Brendon J. Brewer, David W. Hogg, Daniel Foreman-Mackey \\ 
\bf{Order subject to change}}

@@

\section{The Unknown Parameters}
The stars are at positions $\{(x_i, 
y_i)\}_{i=1}^n$ and have fluxes $\{f_i\}$. We also include 
hyperparameters, denoted collectively, by $\alpha$, describing the 
distribution of the positions and fluxes of the stars.

\begin{eqnarray} 
p(\{(x_i, y_i, f_i)\} | \alpha) &=&
\prod_{i=1}^n p(x_i, y_i, f_i | \alpha) \\
&=& \prod_{i=1}^n p(x_i, y_i | \alpha)p(f_i | \alpha) 
\end{eqnarray}
Here, we have assumed that the ``luminosity function'' 
(distribution of fluxes) does not depend on position.

In summary, the unknown parameters are $\{(x_i, y_i, f_i)\}_{i=1}^n$
and $\alpha$.
